---
title: "How to use flashbackscrapR for scraping entire sections"
author: "Felix Lennert"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flashbackscrapR-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
knitr::opts_chunk$set(include = TRUE)
library(flashbackscrapR)
```

# Introduction

Sometimes you may find yourself in the situation that you want to scrape full sections and all of their threads. This is what the functions that start with the prefix `get_full_` are made for: they allow you to get the section and thread suffixes for entire sections. Both functions are complementary: `get_full_section_subs`returns a tibble that can -- with slight modifications -- be passed on to `get_full_thread_links`. You may also want to store the scraping results in a folder structure that is akin to the structure the sub- and sub-sub-sections have on flashback. The `get_full_` functions enable you to do this by automatically creating a folder name according to the section names which can then be passed on to `scrape_thread_content`. Once the scraping process is finished, you will want to combine the content of the respective sections into one .csv file per section. The `bind_section_files` will do the job for you. 
